---
title: "T2 features added diagnostic value"
author: "Cristina Gallego"
date: "March 14, 2016"
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
    theme: cerulean
---

- This uses tree-ensembles based T2 features in addition to the relevant and tentative T1+T2w features
- This code analysis T2w added diagnostic value by comparing with ensembles of only T1w DCE-based features
- T2w discrimination ability (added pAUC ROC value)

```{r setupParent}
knitr::opts_chunk$set(cache=TRUE, cache.path = "parent_cache/", fig.path="parent_figure/")
```


```{r set-options, cache=FALSE, message=FALSE}
options(width = 135)

library(caret)
require(ggplot2)
library("RSQLite")
library(klaR)
library(pROC)
library("Boruta")
require(data.table)
library(RRF)
library(R.utils)
library(MASS)
library(rpart)
library(rpart.plot)
library(adabag)
library(R.utils)

loppath = "C:/Users/windows/Documents/repoCode-local/T2wR/lop_3Dtex_T2w_addedvalue/"
setwd(loppath)
source("functions.R")

## Add LMSIR predicted and T2wBIRADS predicted
LMSIR_lop <- loadToEnv(("Inputs/finalregressorsLMSIR_T2w.RData"))[["LMSIR_lop"]]; 
perfT2wSI_lop <- loadToEnv(("Inputs/final_classifierT2wSI_boosting.RData"))[["perfT2wSI_lop"]]; 

bestune_imgT2 <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["bestune_imgT2"]];
rfbestune_imgT2 <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["rfbestune_imgT2"]];
bestune_allT2 <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["bestune_allT2"]];
rfbestune_allT2 <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["rfbestune_allT2"]];
bestune_imgT1only <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["bestune_imgT1only"]];
rfbestune_imgT1only <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["rfbestune_imgT1only"]];
bestune_T1T2 <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["bestune_T1T2"]];
rfT1T2rfcvperf <- loadToEnv(("Inputs/T2_addeddiagvalue_params_wbagging.RData"))[["rfT1T2rfcvperf"]];


``` 

bagging or boosting for final CAD ensembles? compare cv.errors
===========
```{r baggingorboosting}

## from previous cv parameters
# print winner between 
if(bestune_imgT2$cv.error <= rfbestune_imgT2$cv.error[1]){
  print(cbind(bestune_imgT2, "boosting"))
}else{
  print(cbind(rfbestune_imgT2, "bagging"))
}

# print winner between 
if(bestune_allT2$cv.error <= rfbestune_allT2$cv.error[1]){
  print(cbind(bestune_allT2, "boosting"))
}else{
  print(cbind(rfbestune_allT2, "bagging"))
}

# print winner between 
if(bestune_imgT1only$cv.error <= rfbestune_imgT1only$cv.error[1]){
  print(cbind(bestune_imgT1only, "boosting"))
}else{
  print(cbind(rfbestune_imgT1only, "bagging"))
}

# print winner between 
if(bestune_T1T2$cv.error <= rfT1T2rfcvperf$cv.error[1]){
  print(cbind(bestune_T1T2, "boosting"))
}else{
  print(cbind(rfT1T2rfcvperf, "bagging"))
}


```



kf-cv final performance comparison (3Dtext vs 2Dtex)
=================================
```{r kf-cv, fig.width=12, fig.height=12, warning=FALSE}
# 1) From 100% dataset, Create train/validation (80%) / heldout (20%) partitions
sqlite <- dbDriver("SQLite")
conn <- dbConnect(sqlite, "textureUpdatedFeatures.db")

# 2) all T1w features
lesionsQuery <- dbGetQuery(conn, "SELECT *
         FROM  stage1features
           INNER JOIN lesion ON (stage1features.lesion_id = lesion.lesion_id)
           INNER JOIN f_T2 ON (stage1features.lesion_id = f_T2.lesion_id)")
 
# For bootstrap resampling, createResample is used
# Randomization is done at the patient level, so that bootstrapping preserves lesion independence
lesionsQuery = subset(lesionsQuery, lesion_label != "fociB" & lesion_label != "fociM" ) # exclude foci at this point
id_cad_pts = lesionsQuery$cad_pt_no_txt
uniq_cad = unique(lesionsQuery$cad_pt_no_txt)
npatients = 1:length(uniq_cad)
  
# when y is a factor in an attempt to balance the class distributions within the splits.
# The names of the list objects will denote the fold membership using the pattern 
# resamples." meaning the ith section (of k) of the jth cross-validation set (of times).
set.seed(1234)
npatients = length(uniq_cad)
kfcvpartitionsetD <- createFolds(y = 1:length(uniq_cad),## the outcome data are needed
                                k = 10, 
                                list = TRUE)

save(kfcvpartitionsetD, npatients, uniq_cad, id_cad_pts,
     file="C:/Users/windows/Documents/repoCode-local/T2wR/lop_3Dtex_T2w_addedvalue/Inputs/kfcvpartitionsetD")

```


```{r bringIn3Dtex-boost, child="3Dtex-boost.Rmd"}
 
```
 
```{r bringIn2Dtex-boost, child="2Dtex-boost.Rmd"}
 
```
 




```{r}
save.image("Outputs/CADT2_addeddiagvalue_10fcvboosting.RData")
```



