---
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
---

T2 features 
========================================================

- This code analysis T2w feature relevance, in addition to T1w and T1+T2w 
- finds relevant features via regularized RF
- Plot z-scores via boruta

```{r set-options, echo=FALSE, cache=FALSE}
options(width=95)
setwd("C:/Users/windows/Documents/repoCode-local/T2wR/lop_3Dtex_T2w_addedvalue")
source('C:/Users/windows/Documents/repoCode-local/T2wR/lop_3Dtex_T2w_addedvalue/functions.R')

library("RSQLite")
library(MASS)
library(caret)
require(data.table)
require(ggplot2)
library(pROC)
library(RRF)

# 1) From 100% dataset, Create train/validation (80%) / heldout (20%) partitions
sqlite <- dbDriver("SQLite")
conn <- dbConnect(sqlite, "textureUpdatedFeatures.db")

# 2) all T1w features
lesionsQuery <- dbGetQuery(conn, "SELECT *
         FROM  stage1features
           INNER JOIN lesion ON (stage1features.lesion_id = lesion.lesion_id)
           INNER JOIN f_T2 ON (stage1features.lesion_id = f_T2.lesion_id)")
 
# For bootstrap resampling, createResample is used
# Randomization is done at the patient level, so that bootstrapping preserves lesion independence
lesionsQuery = subset(lesionsQuery, lesion_label != "fociB" & lesion_label != "fociM" ) # exclude foci at this point
id_cad_pts = lesionsQuery$cad_pt_no_txt
uniq_cad = unique(lesionsQuery$cad_pt_no_txt)
npatients = 1:length(uniq_cad)
  
# when y is a factor in an attempt to balance the class distributions within the splits.
# The names of the list objects will denote the fold membership using the pattern 
# resamples." meaning the ith section (of k) of the jth cross-validation set (of times).
set.seed(1234)
npatients = length(uniq_cad)
allpartitionsetD <- createFolds(y = 1:length(uniq_cad),## the outcome data are needed
                                k = npatients, 
                                list = TRUE)  

save(lesionsQuery, id_cad_pts, uniq_cad, allpartitionsetD, 
     file="C:/Users/windows/Documents/repoCode-local/T2wR/lop_3Dtex_T2w_addedvalue/Inputs/allpartitionsetD")



```     


```{r fig.width=12}
# read datasets
T1wf = read_T1uniqcad_parti(id_cad_pts, uniq_cad, allpartitionsetD, npatients, 1)
T2wf = read_T2uniqcad_parti(id_cad_pts, uniq_cad, allpartitionsetD, npatients, 1)
T1T2wf = read_T1T2uniqcad_parti(id_cad_pts, uniq_cad, allpartitionsetD, npatients, 1)
    
## formant
T1wfeatures = rbind(T1wf[[1]], T1wf[[2]])
T1wlesioninfo = rbind(T1wf[[5]], T1wf[[6]])

T2wfeatures = rbind(T2wf[[1]], T2wf[[2]])
T2wlesioninfo = rbind(T2wf[[5]], T2wf[[6]])

T1T2wfeatures = rbind(T1T2wf[[1]], T1T2wf[[2]])
T1T2wlesioninfo = rbind(T1T2wf[[5]], T1T2wf[[6]])


### print number of total lesions 
# before was ##   C / NC = 140 / 132
print(summary(as.factor(T1wfeatures$orig_label)))

# print number T1w features
print(colnames(T1wfeatures))
# print number T2w features
print(colnames(T2wfeatures))
# print number T1+T2w features
print(colnames(T1T2wfeatures))


################ 
## Subset feature selection via rff
################ 
subfeatsel_T1w = subset_feature_selection(T1wfeatures[,-c(ncol(T1wfeatures))]) # exlude orig_label
subfeatsel_T2w = subset_feature_selection(T2wfeatures[,-c(ncol(T2wfeatures))]) # exlude orig_label
subfeatsel_T1T2w = subset_feature_selection(T1T2wfeatures[,-c(ncol(T1T2wfeatures))]) # exlude orig_label

# append
allrfsfeatures = data.frame()
# only t1
df = subfeatsel_T1w$selvarImp
df$SelectedFeatureGroup = "T1wf"
allrfsfeatures = rbind(allrfsfeatures, df)
# only t2
df = subfeatsel_T2w$selvarImp
df$SelectedFeatureGroup = "T2wf"
allrfsfeatures = rbind(allrfsfeatures, df)
# t1 + t2
df = subfeatsel_T1T2w$selvarImp
df$SelectedFeatureGroup = "T1T2wf"
allrfsfeatures = rbind(allrfsfeatures, df)

library("lattice")
library("latticeExtra")
require(ggplot2)

# plot
g <- ggplot(allrfsfeatures, aes(x = factor(selfeat), weight=Overall, fill=SelectedFeatureGroup))
g + geom_bar() + coord_flip() + theme_bw(base_size = 16) + labs(title = "Selected features with RFS B vs. M lesions", 
    x = "", y = "variable importance ranking")

```


Random Forest via permutation tests feature relevance (Boruta)
=====
```{r fig.width=10, fig.height=12}
library("Boruta")
require(data.table)
# Color codes: c('green', 'yellow', 'red', 'blue'), Confirmed, Tentative,
# Rejected and shadow.  Blue boxplots correspond to minimal, average and
# maximum Z score of a shadow attribute. Red Boruta mass: (to run boruta
# uncomment)
set.seed(1)
T1wBoruta <- Boruta(lesion_label ~ ., data = na.omit(T1wfeatures[,-ncol(T1wfeatures)]), 
                    doTrace = 2, ntree = 500)
print(T1wBoruta)
plot(T1wBoruta)

# T2wBoruta:
set.seed(2)
T2wBoruta <- Boruta(lesion_label ~ ., data = na.omit(T2wfeatures[,-ncol(T2wfeatures)]), 
                      doTrace = 2, ntree = 500)
print(T2wBoruta)
plot(T2wBoruta)

# T1T2wBoruta:
set.seed(12)
T1T2wBoruta <- Boruta(lesion_label ~ ., data = na.omit(T1T2wfeatures[,-ncol(T1T2wfeatures)]), 
                      doTrace = 2, ntree = 500)
print(T1T2wBoruta)
plot(T1T2wBoruta)

## Process results and plot Z-scores
library("caret")
confirmedT1w <- T1wBoruta$finalDecision[T1wBoruta$finalDecision == "Confirmed"]
tentativeT1w <- T1wBoruta$finalDecision[T1wBoruta$finalDecision == "Tentative"]
selborutaT1w = c(confirmedT1w, tentativeT1w)
print(paste("Selected T1wBoruta features: ",names(selborutaT1w)))
rankingsT1w <- T1wBoruta$ImpHistory

confirmedT2w <- T2wBoruta$finalDecision[T2wBoruta$finalDecision == "Confirmed"]
tentativeT2w <- T2wBoruta$finalDecision[T2wBoruta$finalDecision == "Tentative"]
selborutaT2w = c(confirmedT2w, tentativeT2w)
print(paste("Selected T2wBoruta features: ",names(selborutaT2w)))
rankingsT2w <- T2wBoruta$ImpHistory

confirmedT1T2w <- T1T2wBoruta$finalDecision[T1T2wBoruta$finalDecision == "Confirmed"]
tentativeT1T2w <- T1T2wBoruta$finalDecision[T1T2wBoruta$finalDecision == "Tentative"]
selborutaT1T2w = c(confirmedT1T2w, tentativeT1T2w)
print(paste("Selected T1T2wBoruta features: ",names(selborutaT1T2w)))
rankingsT1T2w <- T1T2wBoruta$ImpHistory

# get mean z-scores across runs
# only T1w
zscores = rankingsT1w[, names(selborutaT1w)]
df = data.frame(zscores=apply(zscores, 2, mean))
df$selfeatures = rownames(df)
df$SelectedFeatureGroup = "T1wf"
# append
allBorutafeatures = data.frame()
# only t1
allBorutafeatures = rbind(allBorutafeatures, df)

# only T2w
zscores = rankingsT2w[, names(selborutaT2w)]
df = data.frame(zscores=apply(zscores, 2, mean))
df$selfeatures = rownames(df)
df$SelectedFeatureGroup = "T2wf"
# append only T2w
allBorutafeatures = rbind(allBorutafeatures, df)

# only T1T2w
zscores = rankingsT1T2w[, names(selborutaT1T2w)]
df = data.frame(zscores=apply(zscores, 2, mean))
df$selfeatures = rownames(df)
df$SelectedFeatureGroup = "T1T2wf"
# append only T2w
allBorutafeatures = rbind(allBorutafeatures, df)

library("lattice")
library("latticeExtra")
require(ggplot2)

# plot
g <- ggplot(allBorutafeatures, aes(x = factor(selfeatures), weight=zscores, fill=SelectedFeatureGroup))
g + geom_bar() + coord_flip() + theme_bw(base_size = 16) + labs(title = "Selected features with Boruta B vs. M lesions", 
    x = "", y = "z-score")


```


Now correlate with BIRADS T2w descriptors (when available)
====
```{r fig.width=10, fig.height=12}
BIRADS_T2features <- na.omit(T2wfeatures)
BIRADS_T1T2features <- na.omit(T1T2wfeatures)
BIRADS_T2features$find_t2_signal_int <- as.factor(BIRADS_T2features$find_t2_signal_int)
print(summary(BIRADS_T2features$find_t2_signal_int))
BIRADS_T1T2features$find_t2_signal_int <- as.factor(BIRADS_T1T2features$find_t2_signal_int)

# select only confirmed
BIRADS_T2features = BIRADS_T2features[,c("find_t2_signal_int",names(confirmedT2w))]
BIRADS_T1T2features = BIRADS_T1T2features[,c("find_t2_signal_int",names(confirmedT1T2w))]

library(lattice)
super.sym <- trellis.par.get("superpose.symbol")
print("For T2w only:")
#plot
splom(~BIRADS_T2features, groups = find_t2_signal_int, 
    data = BIRADS_T2features, key = list(title = "only T2w relevant features by BIRADS descriptors", 
        columns = 3, points = list(pch = super.sym$pch[c(1:4)], bg = super.sym$col[c(1:4)], 
            col = super.sym$col[c(1:4)], fill = super.sym$col[c(1:4)]), text = list(c("Hyperintense", 
            "Hypointense or not seen", "Isointense or None", "Slightly hyperintense"))))
####
splom(~BIRADS_T1T2features, groups = find_t2_signal_int, 
      data = BIRADS_T1T2features, key = list(title = "T1+T2 relevant features by BIRADS descriptors", 
        columns = 3, points = list(pch = super.sym$pch[c(1:4)], bg = super.sym$col[c(1:4)], 
            col = super.sym$col[c(1:4)], fill = super.sym$col[c(1:4)]), text = list(c("Hyperintense", 
            "Hypointense or not seen", "Isointense or None", "Slightly hyperintense"))))

```

Now feature selection via Regularized Random Forest (RRF) - correct for high ly correlated features
======
```{r fig.width=10, fig.height=12}
library(RRF)
### for T1
T1wXfs = na.omit(T1wfeatures[,-ncol(T1wfeatures)])
T1wYs = T1wXfs$lesion_label
T1wXfs = T1wXfs[,-1]

set.seed(1)
bestmtry = tuneRRF(T1wXfs, T1wYs, mtryStart = 1, ntreeTry=1000, doBest=FALSE, plot=FALSE)
mtryind = which.min(as.data.frame(bestmtry)$OOBError)
T1wfs_rrf = RRF(T1wXfs, T1wYs, mtry=bestmtry[mtryind], flagReg = 1, 
             ntree=2000, 
             localImp=TRUE,
             proximity=TRUE)
print(T1wfs_rrf)

# overall feature importance
T1wvarImp_rrf = data.frame(varImpPlot(T1wfs_rrf, sort=TRUE))
# sort features by MeanDecAccuracy
T1wvarImp <- T1wvarImp_rrf[ order(-T1wvarImp_rrf[,1]), ] 
# pick only non-zero variables
T1wvarImp = unique(T1wvarImp)
df = data.frame(selfeat=rownames(T1wvarImp))
df$MeanDecreaseAccuracy = T1wvarImp$MeanDecreaseAccuracy 
df$SelectedFeatureGroup = "T1wf"
# append
allRRFfeatures = data.frame()
# only t1
allRRFfeatures = rbind(allRRFfeatures, df)


### for T2
T2wXfs = na.omit(T2wfeatures[,-ncol(T2wfeatures)])
T2wYs = T2wXfs$lesion_label
T2wXfs$find_t2_signal_int = as.factor(T2wXfs$find_t2_signal_int)
T2wXfs = T2wXfs[,-1]

set.seed(2)
T2wfs_rrf = RRF(T2wXfs, T2wYs, mtry=1, flagReg = 1, 
             ntree=2000, 
             localImp=TRUE,
             proximity=TRUE)
print(T2wfs_rrf)

# overall feature importance
T2wvarImp_rrf = data.frame(varImpPlot(T2wfs_rrf, sort=TRUE))
# sort features by MeanDecAccuracy
T2wvarImp <- T2wvarImp_rrf[ order(-T2wvarImp_rrf[,1]), ] 
# pick only non-zero variables
T2wvarImp = unique(T2wvarImp)
df = data.frame(selfeat=rownames(T2wvarImp))
df$MeanDecreaseAccuracy = T2wvarImp$MeanDecreaseAccuracy 
df$SelectedFeatureGroup = "T2wf"
# append
# only t2
allRRFfeatures = rbind(allRRFfeatures, df)

### for T1+T2
T1T2wXfs = na.omit(T1T2wfeatures[,-ncol(T1T2wfeatures)])
T1T2wYs = T1T2wXfs$lesion_label
T1T2wXfs$find_t2_signal_int = as.factor(T1T2wXfs$find_t2_signal_int)
T1T2wXfs = T1T2wXfs[,-1]

set.seed(2)
T1T2wfs_rrf = RRF(T1T2wXfs, T1T2wYs, mtry=1, flagReg = 1, 
             ntree=2000, 
             localImp=TRUE,
             proximity=TRUE)
print(T1T2wfs_rrf)

# overall feature importance
T1T2wvarImp_rrf = data.frame(varImpPlot(T1T2wfs_rrf, sort=TRUE))
# sort features by MeanDecAccuracy
T1T2wvarImp <- T1T2wvarImp_rrf[ order(-T1T2wvarImp_rrf[,1]), ] 
# pick only non-zero variables
T1T2wvarImp = unique(T1T2wvarImp)
df = data.frame(selfeat=rownames(T1T2wvarImp))
df$MeanDecreaseAccuracy = T1T2wvarImp$MeanDecreaseAccuracy 
df$SelectedFeatureGroup = "T1T2wf"
# append
# only t2
allRRFfeatures = rbind(allRRFfeatures, df)


library("lattice")
library("latticeExtra")
require(ggplot2)

# plot
g <- ggplot(allRRFfeatures, aes(x = factor(selfeat), weight=MeanDecreaseAccuracy, fill=SelectedFeatureGroup))
g + geom_bar() + coord_flip() + theme_bw(base_size = 16) + labs(title = "Selected features with RRF B vs. M lesions", 
    x = "", y = "MeanDecreaseAccuracy")


```


